Making Multiple Dice Work as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-09 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Adding square/tall FPGA figures.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4528 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

%   - Impact of aspect ratio
\subsection{Impact of Aspect Ratio}
\label{aspect_ratio_impact}
TODO: Javeed
We investigated the implications of the device aspect ratio on routability for the four-partition case. In particular, we compared a device with a square interposer (four rectangular dice) to a device with a rectangular interposer (four square dice.) We used the best CAD flow from Section \ref{sec:partitioner_stage_results} and the best architecture parameters from this section. The results are shown in Table \ref{table:squares}.

>>>>

%   - Impact of aspect ratio
\subsection{Impact of Aspect Ratio}
\label{aspect_ratio_impact}
TODO: Javeed
We investigated the implications of the device aspect ratio on routability for the four-partition case. In particular, we compared a device with a square interposer (four rectangular dice) to a device with a rectangular interposer (four square dice), as shown in \ref{fig:square_tall}. We used the best CAD flow from Section \ref{sec:partitioner_stage_results} and the best architecture parameters from this section. The results are shown in Table \ref{table:squares}.

\begin{figure}[!htbp]
\centering
\subfigure[]{\includegraphics[height = 5cm]{square_fpga.pdf}}
\subfigure[]{\includegraphics[height = 5cm]{tall_fpga.pdf}}
\caption{Devices with (a) a square interposer and (b) square dice.}
\label{fig:square_tall}
\end{figure}
